---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Model parameterisation

### Units

[https://swmm5.org/2019/01/20/refactoring-the-swmm-5-help-file-projects-in-swmm5](https://swmm5.org/2019/01/20/refactoring-the-swmm-5-help-file-projects-in-swmm5)


# Install KWB package 'kwb-r/kwb.swmm' from GitHub
remotes::install_github("kwb-r/kwb.swmm", dependencies = TRUE)

```

## Define paths

```{r define_paths}
# Load the R package
library(kwb.swmm)

### define paths
paths_list <- list(
  cloud_dir = "projects/swmm_workshop/data",
  file_rain = "timeseries_dahlem_5min_60_Jahre.txt",
  path_rain = "<cloud_dir>/<file_rain",
  model_dir =  kwb.swmm::extdata_file("models/workshop"),
  model_name = "Testgebiet_imp",
  model_inp = "<model_dir>/<model_name>.inp",
  model_out = "<model_dir>/<model_name>.out",
  model_rpt = "<model_dir>/<model_name>.rpt",
  swmm_dir = "C:/_UserProg/EPA SWMM 5.1.015",
  swmm_exe = "<swmm_dir>/swmm5.exe"
)

paths <- kwb.utils::resolve(paths_list)

paths
```

## SWMM Files

This tutorial needs a few `climate` files which can be provided [locally](#locally)
from a predefined folder on your Windows computer or directly downloaded from
the KWB [Cloud](#cloud). Within this tutorial the latter approach is used. 

Currently one climate input file (rain) and a SWMM `.inp` file are required:

* `<model_name>`.`inp` (input: SWMM model, prepared using SWMM-GUI, here: `r paths$model_path`)

* `<rain-data>`.`txt` (input: rain data)


### Locally

Copy the content of the KWB cloud folder `r paths$cloud_dir` to `paths$model_dir` (here: `r paths$model_dir`).

### Cloud 

You can download the required model files from the KWB cloud if you are a 
registered user with access to the folder ``r paths$cloud_dir``

For doing so follow the steps below: 

1. Open `RStudio` and run `usethis::edit_r_environ()`

2. In the opened window add the required environment variables

```
NEXTCLOUD_URL = "https://<replace-with-dwc-cloud-url>"
NEXTCLOUD_USER = "<your-dwc-cloud-username>" # your username
NEXTCLOUD_PASSWORD = "your-nextcloud-app-password" ### see details below
```

For creating `<your-nextcloud-app-password>`:

* go to: https://replace-with-dwc-cloud-url/index.php/settings/user/security

* scroll down to `create new app password`

* select a name e.g. `r-script` and copy the token and replace `your-nextcloud-app-password`


3. Finally you need to restart Rstudio and proceed with the code below:

```{r nextcloud_download, eval = FALSE}



# Download rain data
swmm_climate_files <- kwb.nextcloud::list_files(
  paths$cloud_dir,
  full_info = TRUE) %>% 
  dplyr::filter(file == paths$file_rain)

kwb.nextcloud::download_files(href = swmm_climate_files$href,
                              target_dir = paths$model_dir)

```

# Run SWMM

```{r run_swmm, eval = FALSE}
# run andi`s model 
swmmr::run_swmm(inp = paths$model_inp,
                rpt = paths$model_rpt,
                out = paths$model_out,
                exec = paths$swmm_exe)
                
swmm_inp <- swmmr::read_inp(paths$model_inp)


```
