---
title: "SWMM Python"
author: "Michael Rustler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SWMM Python}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
is_ghactions <- identical(Sys.getenv("CI"), "true")
```
## Prerequisites 

Install [Anaconda](https://www.anaconda.com/products/individual) on your computer
(**requires admin rights!**): 
[https://www.anaconda.com/products/individual#Downloads](https://www.anaconda.com/products/individual#Downloads)

Or [Miniconda](https://docs.conda.io/en/latest/miniconda.html) with `kwb.python::install_miniconda()` (no admin rights required).

For this tutorial [Miniconda](https://docs.conda.io/en/latest/miniconda.html) is 
used.


## Install miniconda

```{r install_miniconda, eval = is_ghactions}
kwb.python::install_miniconda()
```

## Install pywmm

### pyswmm_v1.0.1

Setup an environment named `swmm_py` for where we want to install [pyswmm v1.0.1](https://pyswmm.readthedocs.io/en/latest/) 

DOES NOT WORK currently!

```{r pyswmm_v101, eval = FALSE}
### Create python environment 

### Use Python 3.8 (as for 3.9 installation of "pyswmm" requires 
### Microsoft Visual Studio 2017: "Building windows wheels for Python 3.9 requires 
### Microsoft Visual Studio 2017 Get it with "Visual Studio 2017ยง


################################################################################
### Install "pyswmm" (v1.0.1 available, status:2021-01-25)
### https://pypi.org/project/pyswmm/ 
################################################################################

### Downgrade dependency "aenum" to get rid of error: 
### reticulate::import("pyswmm") 
### Error in py_module_import(module, convert = convert) : 
### NameError: name 'US' is not defined
### https://github.com/OpenWaterAnalytics/pyswmm/issues/272#issuecomment-782697886
### should be fixed in next release of "swmm-toolkit" (v0.9.0)
### https://github.com/OpenWaterAnalytics/swmm-python/pull/67

kwb.python::conda_py_install(env_name = "swmm_py", 
                             pkgs = list(conda = c("python=3.8"), 
                                         py = c("pyswmm", "aenum==2.2.6")))

pyswmm <- reticulate::import("pyswmm", convert = TRUE)
#Fehler in py_module_import(module, convert = convert) : 
# ImportError: DLL load failed while importing _solver: 
# The entered module was not found.

### check pyswmm version (should be v1.0.1 as installed using "pip") 
#pyswmm$VERSION_INFO
```

### pyswmm_v0.6.2

Setup an environment named `swmm_conda` for where we want to install [pyswmm v0.6.2](https://pyswmm.readthedocs.io/en/latest/) 

```{r pyswmm_v062, eval = is_ghactions}
################################################################################
### Install "pyswmm" (v0.6.2 available, status:2021-01-25)
### https://pypi.org/project/pyswmm/ 
################################################################################

kwb.python::conda_py_install(env_name = "swmm_conda", 
                             pkgs = list(conda = c("python=3.8", "pyswmm"), 
                                         py = NULL))


pyswmm <- reticulate::import("pyswmm")
### check pyswmm version (should be v0.6.2 as installed using "conda") 
pyswmm$VERSION_INFO

path_swmm_inp <- kwb.swmm::extdata_file("models/green-roof_neubrandenburg/neubrand.inp")


withr::with_dir(new = dirname(path_swmm_inp), 
                code = {
sim <- pyswmm$Simulation(inputfile = basename(path_swmm_inp),
                         reportfile = "neubrand.rpt",
                         outputfile = "neubrand.out")
                  }
)

sim$engine_version
sim$system_units
sim$flow_units
sim$engine_version
sim$execute()
sim$runoff_error

swmm_lib <- "C:/_UserProg/EPA SWMM 5.1.015/swmm5.dll"
if(file.exists(swmm_lib)) {
 
 pyswmm$lib$use(swmm_lib)
 
withr::with_dir(new = dirname(path_swmm_inp), 
                code = {
sim <- pyswmm$Simulation(inputfile = basename(path_swmm_inp),
                         reportfile = "neubrand.rpt",
                         outputfile = "neubrand.out")
                  }
) 
## Errors with: 
## Fehler in py_call_impl(callable, dots$args, dots$keywords) : 
## OSError: [WinError 193] %1 ist keine zulaessige Win32-Anwendung
## open issue: https://github.com/OpenWaterAnalytics/pyswmm/issues/224

}


```


## Dependencies

### R  

```{r session_info_local, echo = !is_ghactions, eval = FALSE}
sessioninfo::session_info()
- Session info -------------------------------------------------------------------------------------------
 setting  value                       
 version  R version 4.0.4 (2021-02-15)
 os       Windows 10 x64              
 system   x86_64, mingw32             
 ui       RStudio                     
 language (EN)                        
 collate  German_Germany.1252         
 ctype    German_Germany.1252         
 tz       Europe/Berlin               
 date     2021-03-25                  

- Packages -----------------------------------------------------------------------------------------------
 package     * version date       lib source        
 assertthat    0.2.1   2019-03-21 [1] CRAN (R 4.0.2)
 cli           2.3.1   2021-02-23 [1] CRAN (R 4.0.2)
 digest        0.6.27  2020-10-24 [1] CRAN (R 4.0.3)
 evaluate      0.14    2019-05-28 [1] CRAN (R 4.0.2)
 glue          1.4.2   2020-08-27 [1] CRAN (R 4.0.2)
 htmltools     0.5.1.1 2021-01-22 [1] CRAN (R 4.0.3)
 jsonlite      1.7.2   2020-12-09 [1] CRAN (R 4.0.3)
 knitr         1.31    2021-01-27 [1] CRAN (R 4.0.4)
 lattice       0.20-41 2020-04-02 [1] CRAN (R 4.0.3)
 Matrix        1.3-2   2021-01-06 [2] CRAN (R 4.0.4)
 rappdirs      0.3.3   2021-01-31 [1] CRAN (R 4.0.3)
 Rcpp          1.0.6   2021-01-15 [1] CRAN (R 4.0.3)
 reticulate    1.18    2020-10-25 [1] CRAN (R 4.0.3)
 rlang         0.4.10  2020-12-30 [1] CRAN (R 4.0.3)
 rmarkdown     2.7     2021-02-19 [1] CRAN (R 4.0.4)
 sessioninfo   1.1.1   2018-11-05 [1] CRAN (R 4.0.3)
 withr         2.4.1   2021-01-26 [1] CRAN (R 4.0.3)
 xfun          0.22    2021-03-11 [1] CRAN (R 4.0.4)
 yaml          2.2.1   2020-02-01 [1] CRAN (R 4.0.2)

[1] C:/Users/mrustl/Documents/R/win-library/4.0
[2] C:/Program Files/R/R-4.0.4/library

```

```{r session_info_gh, eval = is_ghactions}
sessioninfo::session_info()
```

### Conda Environment Yaml 

pyswmm v1.0.1 (from [PyPi](https://pypi.org/project/pyswmm/))

```
name: swmm_py
channels:
  - conda-forge
  - defaults
dependencies:
  - aenum=2.2.6=pyhd3deb0d_0
  - ca-certificates=2020.12.5=h5b45459_0
  - certifi=2020.12.5=py38haa244fe_1
  - openssl=1.1.1k=h8ffe710_0
  - pip=21.0.1=pyhd8ed1ab_0
  - python=3.8.8=h7840368_0_cpython
  - python_abi=3.8=1_cp38
  - setuptools=49.6.0=py38haa244fe_3
  - sqlite=3.35.4=h8ffe710_0
  - vc=14.2=hb210afc_4
  - vs2015_runtime=14.28.29325=h5e1d092_4
  - wheel=0.36.2=pyhd3deb0d_0
  - wincertstore=0.2=py38haa244fe_1006
  - pip:
    - pyswmm==1.0.1
    - swmm-toolkit==0.8.1
prefix: C:\Users\mrustl\AppData\Local\r-miniconda\envs\swmm_py

```


**pyswmm v0.6.2** (from [conda-forge](https://anaconda.org/conda-forge/pyswmm))


```{r conda_env_swmm_conda1, echo = is_ghactions, eval = FALSE}
name: swmm_conda
channels:
  - conda-forge
  - defaults
dependencies:
  - ca-certificates=2020.12.5=h5b45459_0
  - certifi=2020.12.5=py38haa244fe_1
  - llvm-openmp=8.0.1=h1ad3211_0
  - openmp=8.0.1=0
  - openssl=1.1.1k=h8ffe710_0
  - pip=21.0.1=pyhd8ed1ab_0
  - pyswmm=0.6.2=pyh9f0ad1d_1
  - python=3.8.8=h7840368_0_cpython
  - python_abi=3.8=1_cp38
  - setuptools=49.6.0=py38haa244fe_3
  - six=1.15.0=pyh9f0ad1d_0
  - sqlite=3.35.2=h8ffe710_0
  - swmm=5.2.1=ha925a31_1
  - vc=14.2=hb210afc_4
  - vs2015_runtime=14.28.29325=h5e1d092_4
  - wheel=0.36.2=pyhd3deb0d_0
  - wincertstore=0.2=py38haa244fe_1006
prefix: C:\Users\mrustl\.conda\envs\swmm_conda
```

```{r conda_env_swmm_conda2, echo = !is_ghactions, eval = !is_ghactions}
path_environment_yml <- kwb.python::conda_export("swmm_conda")
path_environment_yml
cat(paste0(readLines(path_environment_yml), collapse = "\n"))
```

